### 2023-07-20 main.tex
cleanUpIII
add mapping empty-steady state

@@

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
\\&=
(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
we also introduce 
\begin{equation}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

@@

>>>>

\begin{equation}\label{steadyS-SECOND-def}

@@

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
\end{split}
\end{equation}
\begin{equation}
	\begin{split}
\boxed{Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}}
\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
we also introduce 
\begin{equation}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

@@

Considering the empty state as 
	|\Psi_{0}^{0}\rangle:=\begin{pmatrix}
		0\\
		0\\
		1
	\end{pmatrix}\otimes \cdots \otimes\begin{pmatrix}
	0\\
	0\\
	1
then, we can map via $W$ the above vector to the steady state $|\Psi^{''}\rangle$ of $H^{''}$ defined in \eqref{steadyS-SECOND-def}, namely
	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
